---
title: "Tooth Growth rate by varying source of vitamin intake"
author: "Cy"
date: "11/4/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 2

## Overview  
In this section, Exploratory data analysis will be performed on Tooth Growth data. The performance of using Orange Juice and Vitamin C with different dosages are evaluated through statistical inference methodology.
```{r loading,cache=T}
data("ToothGrowth")
summary(ToothGrowth)
head(ToothGrowth,3)
```
### Boxplot for tooth growth
```{r box,cache=T}
data("ToothGrowth")
ToothGrowth$supp<-as.factor(ToothGrowth$supp)
boxplot(len~dose+supp, data=ToothGrowth,col='orange')
```

**Figure above visualize the Tooth Growth Data, Through visual inspection, The Orange Juice has better performance**  

### Hypothesis testing and Confidence Interval
Using T-distribution since each unique case has less samples.  
*Null hypothesis* : Orange Juice has same effect with Vitamin C  
*Alternative hypothesis* : Orange Juice has better effect compared to Vitamin C  
To obtain better data consistency, the dosage was varied and compared to each other  
```{r Conf,cache=T}
# 0.5 Dosage
oj5<-subset(ToothGrowth,supp=="OJ" & dose=="0.5",select =len)
vc5<-subset(ToothGrowth,supp=="VC"& dose=="0.5",select =len)
p5<-t.test(oj5,vc5,paired = FALSE)

# 1 Dosage
oj1<-subset(ToothGrowth,supp=="OJ" & dose=="1",select =len)
vc1<-subset(ToothGrowth,supp=="VC"& dose=="1",select =len)
p1<-t.test(oj1,vc1,paired = FALSE)

# 2 Dosage
oj2<-subset(ToothGrowth,supp=="OJ" & dose=="2",select =len)
vc2<-subset(ToothGrowth,supp=="VC"& dose=="2",select =len)
p2<-t.test(oj2,vc2,paired = FALSE)

result<-data.frame("Dosage 0.5"=c(p5$p.value,p5$conf.int[1],p5$conf.int[2]),
           "Dosage 1.0"=c(p1$p.value,p1$conf.int[1],p1$conf.int[2]),
           "Dosage 2.0"=c(p2$p.value,p2$conf.int[1],p2$conf.int[2]),
           row.names = c("p-value","Lower Confidence Limit","Upper Confidence Limit"))
print(round(result,4))
```
## Conclusion (Part II)  
The p-values for 0.5 and 1.0 dosage are below the threshold 0.05, proving the improvement of using **orange juice** compared to **vitamin C**. However, the p-value for 2.0 dosage is above 0.05 and its lower confidence limit is **below zero**. This may arisen from faulty data or poor methodology of research. Considering cases for 2.0 dosage, null hypothesis cannot be rejected.

## Recommendation   
The experiment should be conducted with more data samples to obtain a much convincing inference with solid evidence.